\documentclass[11pt,a4paper]{article}

% Packages
\usepackage[margin=0.6in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontenc}
\usepackage{helvet}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{parskip}

% Colors
\definecolor{primary}{HTML}{1A5276}
\definecolor{accent}{HTML}{2E86C1}
\definecolor{darkgray}{HTML}{2C3E50}
\definecolor{lightgray}{HTML}{F2F3F4}

% Font
\renewcommand{\familydefault}{\sfdefault}

% Section formatting
\titleformat{\section}{\large\bfseries\color{primary}}{}{0em}{}[\color{accent}\titlerule]
\titlespacing{\section}{0pt}{10pt}{5pt}

% Remove page number
\pagestyle{empty}

% Hyperlink style
\hypersetup{
    colorlinks=true,
    linkcolor=accent,
    urlcolor=accent
}

\begin{document}

% Header
\begin{center}
    {\LARGE\bfseries\color{primary} InfectionIQ}\\[4pt]
    {\large\color{darkgray} AI-Powered Surgical Infection Prevention}\\[3pt]
    {\small\color{darkgray} \textit{``We predict surgical infections before they happen by tracking contamination pathways in real time.''}}
\end{center}

\vspace{-2pt}

% Problem
\section{The Problem}

Hospital-acquired infections (HAIs) affect \textbf{1 in 31} U.S. patients and cost \textbf{\$28{-}45B annually}. Hand hygiene is the single most effective prevention method, yet compliance rates average just \textbf{40{-}60\%}. Current monitoring relies on self-reporting and manual audits, which are unreliable, retroactive, and impossible to scale.

% Solution
\section{Our Solution}

InfectionIQ is a \textbf{real-time computer vision system} that predicts surgical site infections before they happen by tracking contamination pathways during procedures.

\begin{itemize}[leftmargin=1.2em, itemsep=2pt]
    \item \textbf{Vision-only monitoring}: No badges, wearables, or additional hardware. Works with existing camera infrastructure.
    \item \textbf{Real-time detection}: Tracks whether staff sanitize before and after patient contact using CV (YOLOv8, MediaPipe).
    \item \textbf{ML-powered risk prediction}: Ensemble models (XGBoost, LightGBM, CatBoost) predict infection risk before surgery begins.
    \item \textbf{Automated alerts and compliance analytics}: Instant notifications and audit-ready dashboards for hospital administrators.
\end{itemize}

% Market
\section{Market Opportunity}

\begin{tabularx}{\textwidth}{X X}
    \textbf{Target Market} & \textbf{Revenue Model} \\[3pt]
    \small 6,000+ U.S. hospitals (100+ beds) & \small SaaS: \$50K{-}150K/year per facility \\
    \small 5,700+ ambulatory surgery centers & \small 1{-}2\% penetration = \$30{-}180M ARR \\
    \small 15,000+ nursing homes (expansion) & \small Upsell: OR analytics, training insights, insurance risk scoring \\
\end{tabularx}

% Defensibility
\section{Scalability and Defensibility}

\begin{itemize}[leftmargin=1.2em, itemsep=2pt]
    \item \textbf{Zero hardware dependency}: Software-first, deploys on existing infrastructure.
    \item \textbf{Compounding data moat}: Proprietary ML models improve with every facility deployment.
    \item \textbf{Regulatory complexity}: HIPAA and Joint Commission standards create a natural barrier to entry.
    \item \textbf{Expansion path}: Ambulatory surgery centers, nursing homes, long-term care, and international markets.
\end{itemize}

% Traction
\section{Traction and Early PMF Signals}

\begin{itemize}[leftmargin=1.2em, itemsep=2pt]
    \item Working \textbf{live demo}: Real-time CV detection, ML risk scoring, and compliance dashboard.
    \item \textbf{Medical advisor} onboarded.
    \item Consulting with a \textbf{USC professor} with domain expertise on adoption challenges in healthcare.
    \item Active conversations with \textbf{Type One Ventures} and \textbf{Ethosion Capital Partners}.
\end{itemize}

% Team
\section{Team}

\textbf{3-person technical team} out of the University of Southern California, M.S. in Computer Science (AI). Built the entire system end-to-end: CV pipeline, ML ensemble, full-stack dashboard, and real-time API.

InfectionIQ was inspired by a \textbf{personal family experience} with surgical infection. This is not an academic exercise; it is personal conviction backed by technical depth.

% Ask
\section{The Ask}

Currently preparing for our \textbf{pre-seed round} to accelerate development, pursue pilot partnerships with hospitals, and bring InfectionIQ to market.

\vfill

\begin{center}
    \small\color{darkgray}
    \textbf{Parth Gosar} $\mid$ M.S. Computer Science (AI), USC $\mid$ \href{https://psg.bio}{psg.bio}
\end{center}

\end{document}
